Developing a Bubble Chamber Particle Discriminator Using Semi-Supervised Learning

### 2018-08-12 documentation/paper.tex
Added placeholder for abstract; minor fixes

@@

Numerically, This is a variable defined as $C$ below, where $N$ and $A$ are the sets of outputs of the supervised learning discriminator in question, corresponding to the sets of neutrons and alpha particles respectively. It calculates the spread of the network's predictions for each ground truth class. This means that a decisive discriminator, which produces a wide separation between the two classes, is preferred over one that produces a nebulous cloud of outputs with a seemingly arbitrary decision boundary.

@@

Two techniques for semi-supervised learning have been developed for this study: gravitational differentiation and iterative cluster nucleation. The essence of both algorithms is a positive feedback loop. First, the network is trained on a smaller amount of imperfect data. Throughout the training process, the network runs predictions on unlabeled data. By using its most confident predictions are used in the training process, the desired function (separating particle types) is continuously reinforced, while less confident predictions are de-emphasized. This effectively draws new, unlabeled data into the training set.

>>>>

\title{Developing a Bubble Chamber Particle Discriminator Using Semi-Supervised Learning}
\author{Brendon Matusch, X, Y, and Z}
\date{August 2018}
\maketitle

\begin{abstract}
    TODO, once content is affirmed.
\end{abstract}

@@

Numerically, this is a variable defined as $C$ below, where $N$ and $A$ are the sets of outputs of the supervised learning discriminator in question, corresponding to the sets of neutrons and alpha particles respectively. It calculates the spread of the network's predictions for each ground truth class. This means that a decisive discriminator, which produces a wide separation between the two classes, is preferred over one that produces a nebulous cloud of outputs with a seemingly arbitrary decision boundary.

@@

Two techniques for semi-supervised learning have been developed for this study: gravitational differentiation and iterative cluster nucleation. The essence of both algorithms is a positive feedback loop. First, the network is trained on a smaller amount of imperfect data. Throughout the training process, the network runs predictions on unlabeled data. By using its most confident predictions in the training process, the desired function (separating particle types) is continuously reinforced, while less confident predictions are de-emphasized. This effectively draws new, unlabeled data into the training set.
